### 2020-03-03 doc/icfp20/counterpoint.tex
improve glossary

The middle bars of the music should maintain consonance of intervals
and independence of melodic lines.
As we saw before, consonant intervals include the unison,
3rd\footnote{We use ``3rd'' to mean both the major and minor variants
of the 3rd interval, and similarly for the 6th.}, 5th, 6th, and 8th,
and among these, the unison is clearly an obstacle to distinguishing
between the two lines of music.
Therefore, the middle bars must consist only of the latter four intervals.
We encode this rule as the \texttt{checkIntervals} function, which
returns a list of errors corresponding to the occurrences of dissonant
intervals and unisons.

>>>>

The middle bars of the music should maintain consonance of intervals
and independence of melodic lines.
As we saw in Figure~\ref{fig:interval}, consonant intervals include
the unison, 3rd, 5th, 6th, and 8th, and among these, the unison is
clearly an obstacle to distinguishing between the two lines of music.
Therefore, the middle bars must consist only of the latter four intervals.
We encode this rule as the \texttt{checkIntervals} function, which
returns a list of errors corresponding to the occurrences of dissonant
intervals and unisons.

### 2020-03-03 doc/icfp20/music.tex
improve glossary

An \emph{interval} represents the difference in pitch between
two notes.
There are 13 kinds of interval within an octave
(Figure~\ref{fig:interval}), and these intervals can be classified from
several different perspectives:
(i) major or minor; (ii) consonant or dissonant; and (iii) perfect
or imperfect.
We define intervals as a datatype \texttt{Interval}, where each
constructor represents one of the 13 intervals.

>>>>

An \emph{interval} represents the difference in pitch between
two notes.
There are 13 kinds of interval within an octave
(Figure~\ref{fig:interval}), and these intervals can be classified from
several different perspectives:
(i) major or minor; (ii) consonant or dissonant; and (iii) perfect
or imperfect.
We represent intervals as natural numbers, but in this paper, we
refer to them using more informative names such as \texttt{maj3}
and \texttt{per8}.

\paragraph{Chords and Triads}

A \emph{chord} refers to a set of simultaneously sounding notes.
In this paper we are particularly interested in \emph{triads},
which are chords consisting of three notes separated by the 3rd
intervals (i.e., \texttt{maj3} and \texttt{min3}).
We define triads as a datatype \texttt{Triad} with roman numeral
constructors representing the lowest note (called the \emph{root}).
For instance, \texttt{I} in C major represents the triad C-E-G.
